Resolvable Ambiguity

### 2019-07-07 paper/paper.tex
First lines of the abstract.

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Text of abstract \ldots.
\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
% Why?

A traditional view when designing programming languages is that syntax
definitions should be unambiguous: only unambiguous grammars are used to construct
language specific parsers that either rejects a program, or accepts it and
produces a unique parse tree. However,

% Why composing languages
-

% Problem we address
Resolvable ambiguity
Two sub-problems. Static and dynamic resolvability

% Our solution
Prove static resolvable for

% Three case studies

\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{Language Composition, Context Free Grammars, Domain-Specific Languages}  %% \keywords are mandatory in final camera-ready submission
